### 2016-09-12 plosOneJordanousKeller/PAPER/RevisedManuscript.tex
updated SI captions

\subsection*{S1 Appendix}\label{S1_Appendix}
{\bf Creativity Corpus.}  The following 30 papers were used as the {\em creativity corpus} for this work:

@@

\subsection*{S2 Appendix}\label{S2_Appendix}
{\bf Non-Creativity Corpus.} The following 60 papers were used as the {\em non-creativity corpus} for this work:

>>>>

\subsection*{S1 Appendix}\label{S1_Appendix}
{\bf Creativity Corpus.}  These 30 papers were used as the {\em creativity corpus} for this work.

@@

\subsection*{S2 Appendix}\label{S2_Appendix}
{\bf Non-Creativity Corpus.} These 60 papers were used as the {\em non-creativity corpus} for this work.
